Online {\IterComp}

### 2017-09-16 conclusions.tex
minor

\section{Conclusions}
This paper introduced a novel efficiency metric which enables us to compare in terms of performance versions of an application compiled in
different ways even when they perform different amounts of work. Our approach automatically estimates the work done by each basic block of
the application and inserts instrumentation code to increment a global work counter every time a block is executed. We optimize the
placement of the instrumentation probes to reduce the runtime overhead. On top of it, we implement two strategies for removing probes from
the application to control the trade-off between runtime overhead and work estimation accuracy.

>>>>

\section{Conclusions}
This paper has introduced a novel efficiency metric which enables us to compare in terms of performance versions of an application compiled
in different ways even when they perform different amounts of work. Our approach automatically estimates the work done by each basic block
of the application and inserts instrumentation code to increment a global work counter every time a block is executed. We optimize the
placement of the instrumentation probes to reduce the runtime overhead. On top of it, we implement two strategies for removing probes from
the application to control the trade-off between runtime overhead and work estimation accuracy.
